Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-05-21 vesicle_code/docs/adhesion/adhesion.tex
renaming a figure to be consistent with parameter values

Finally, to further characterize the rotating dynamics of a doublet in
the fluid trap, we compute and plot the vorticity and total force on a
doublet with identical vesicles with reduced area $\Delta A=0.7$,
Hamaker constant $\mathcal{H} = 0.7$, separation distance $\delta =
0.4$, and extensional rate $\chi = 0.7$ in
Figure~\ref{fig:extensionalVorticity}.  Starting from an initial inclination angle $\theta=\pi$, the doublet 
starts to rotate around $t\sim 250$.  We notice that the net force on
each vesicle is almost anti-parallel to the diverging flow in the
far-field so to balance the hydrodynamic drag force that pulls the
vesicles apart.  Then, as the doublet starts to rotate, each vesicle
experiences a drag force from the diverging streaming
flows.  
%
For small extensional rate, the rotation continues until
$\theta = \pi/2$ so the doublet remains perfectly symmetric with respect
to their mid-plane, and each vesicle experiences drag forces (from the diverging flow) that cancel
each other.  
%
For slightly higher extensional rate in Figure~\ref{fig:extensionalVorticity}, we observe
that the two vesicles slide against each other (around $t=280$) as the doublet rotates.
The slight sliding motion leads to a transition in the contact region
membrane shape from a bulging profile to an S-shape profile of nearly
uniform height except near the edge of contact region.  This adjustment
greatly reduces the net force on each vesicle, leading to an equilibrium
configuration with an inclination angle $\theta > \pi/2$ as shown in the
left of Figure~\ref{fig:extensionalInclinationAngle}.  Finally, the
vorticity and the flow between the vesicles approaches zero and the
result is a fluid trap containing the doublet.
\begin{figure}[htp]
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity01.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity02.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity03.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity04.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity05.png} \\
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity06.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity07.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity08.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity09.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity10.png}
  \caption{\label{fig:extensionalVorticity} The vorticity and total
  force of two vesicles in a doublet.  The reduced area is $\Delta A =
  0.7$, the separation distance is $\delta = 0.4$, the Hamaker constant
  is $\mathcal{H} = 0.7$, and the extensional rate is $\chi = 0.7$.}
\end{figure}

@@

\begin{figure}
  \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}
  \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
  \includegraphics[height=0.27\textwidth]{figs/shear_adR1em1_ra090_phaseDiagram.pdf}
  \caption{\label{fig:sflow_phase_diagram} {\em Left}: Distance between
  a pair of vesicles in a planar shear flow with shear rate $\chi=0.5$,
  and separation distance $\delta = 0.4$.  The different lines
  correspond to a linear spacing of Hamaker constants ranging from
  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Center and Right}:
  Phase diagram of vesicle hydrodynamics in a shear flow with $\delta =
  0.4$ (center) and $\delta = 0.1$ (right) with reduced area  $\Delta A
  = 0.9$. The critical Hamaker constant $\mathcal{H}$ for binding of two
  vesicles in a shear flow depends on the shear rate $\chi$.  For a
  doublet to form, lower separation distances require a stronger Hamaker
  constants at a given shear rate.}
\end{figure}

>>>>

Finally, to further characterize the rotating dynamics of a doublet in
the fluid trap, we compute and plot the vorticity and total force on a
doublet with identical vesicles with reduced area $\Delta A=0.7$,
Hamaker constant $\mathcal{H} = 0.7$, separation distance $\delta =
0.4$, and extensional rate $\chi = 0.07$ in
Figure~\ref{fig:extensionalVorticity}.  Starting from an initial inclination angle $\theta=\pi$, the doublet 
starts to rotate around $t\sim 250$.  We notice that the net force on
each vesicle is almost anti-parallel to the diverging flow in the
far-field so to balance the hydrodynamic drag force that pulls the
vesicles apart.  Then, as the doublet starts to rotate, each vesicle
experiences a drag force from the diverging streaming
flows.  
%
For small extensional rate, the rotation continues until
$\theta = \pi/2$ so the doublet remains perfectly symmetric with respect
to their mid-plane, and each vesicle experiences drag forces (from the diverging flow) that cancel
each other.  
%
For slightly higher extensional rate in Figure~\ref{fig:extensionalVorticity}, we observe
that the two vesicles slide against each other (around $t=280$) as the doublet rotates.
The slight sliding motion leads to a transition in the contact region
membrane shape from a bulging profile to an S-shape profile of nearly
uniform height except near the edge of contact region.  This adjustment
greatly reduces the net force on each vesicle, leading to an equilibrium
configuration with an inclination angle $\theta > \pi/2$ as shown in the
left of Figure~\ref{fig:extensionalInclinationAngle}.  Finally, the
vorticity and the flow between the vesicles approaches zero and the
result is a fluid trap containing the doublet.
\begin{figure}[htp]
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity01.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity02.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity03.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity04.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity05.png} \\
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity06.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity07.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity08.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity09.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity10.png}
  \caption{\label{fig:extensionalVorticity} The vorticity and total
  force of two vesicles in a doublet.  The reduced area is $\Delta A =
  0.7$, the separation distance is $\delta = 0.4$, the Hamaker constant
  is $\mathcal{H} = 0.7$, and the extensional rate is $\chi = 0.07$.}
\end{figure}

@@

\begin{figure}
  \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1Chi5em1_ra090.pdf}
  \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
  \includegraphics[height=0.27\textwidth]{figs/shear_adR1em1_ra090_phaseDiagram.pdf}
  \caption{\label{fig:sflow_phase_diagram} {\em Left}: Distance between
  a pair of vesicles in a planar shear flow with shear rate $\chi=0.5$,
  and separation distance $\delta = 0.4$.  The different lines
  correspond to a linear spacing of Hamaker constants ranging from
  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Center and Right}:
  Phase diagram of vesicle hydrodynamics in a shear flow with $\delta =
  0.4$ (center) and $\delta = 0.1$ (right) with reduced area  $\Delta A
  = 0.9$. The critical Hamaker constant $\mathcal{H}$ for binding of two
  vesicles in a shear flow depends on the shear rate $\chi$.  For a
  doublet to form, lower separation distances require a stronger Hamaker
  constants at a given shear rate.}
\end{figure}
